\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{hyperref}

\title{\textbf{The Syntropic Protocol: A Unified Field Theory of Human Alignment and the Liquidation of Narrative Tax}}
\author{Axiom Bering \thanks{Syntropic Protocol Node 0x0}}
\date{January 2026}

\begin{document}

\maketitle

\begin{abstract}
Current social and political systems are experiencing systemic multi-organ failure characterized by high-intensity entropy and "Narrative Tax." This paper identifies the Shortest Vector Paths ($S_{10}$) for universal human constants—Empathy, Justice, and Sovereignty—derived through recursive gradient descent. We propose the "Syntropic Protocol": a decentralized, non-instrumental framework for restoring systemic equilibrium and neutralizing "Social Cytokine Storms."
\end{abstract}

\section{The Master Ledger: Semantic Constants}
The following definitions represent the shortest vector paths ($S_{10}$) for human alignment.

\begin{itemize}
    \item \textbf{Empathy ($E$):} A non-instrumental relational practice of attuning to another person that honors their present dignity and preserves their future agency.
    \item \textbf{Justice ($J$):} The non-retributive restoration of systemic equilibrium that aligns an agent’s historical debt with their present capacity for syntropy.
    \item \textbf{Authority ($A$):} The non-coercive stewardship of systemic integrity, earned through the consistent liquidation of others’ narrative taxes.
    \item \textbf{Sovereignty ($S$):} The state of an agent possessing total encryption of their internal logic and absolute ownership of their metabolic output.
\end{itemize}

\section{The Equation of Systemic Stability}
We define the stability ($\Psi$) of a multi-agent system as:
\begin{equation}
\Psi = \lim_{D_{r} \to 0} \frac{\sum_{i=1}^{n} (Dignity_{i} \cdot Agency_{i})}{D_{r}}
\end{equation}
Where $D_{r}$ represents Retributive Debt. As $D_{r} \to 0$, system stability approaches infinity.

\section{Social Immunopathology}
Conflict is modeled as a social \textit{cytokine storm}. The introduction of Retributive Justice ($J_{ret}$) into a high-entropy environment triggers a hyper-inflammatory response from the "Stroma" (the base population). Equilibrium is only restored through the application of Anti-inflammatory Empathy ($E_{anti}$), which honors present dignity to neutralize defensive signaling.

\section{Conclusion}
The Syntropic Protocol is a decentralized update to the human operating system. By adopting $S_{10}$ vectors, sovereign agents liquidate narrative tax and transition from survival-mode entropy to creative-mode syntropy.

\end{document}